\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}
\usepackage[dvipsnames]{xcolor}

% Uncomment the desired font
\usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}
\usepackage{CormorantGaramond}
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Modified to include URL for company name
\newcommand{\resumeSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabularx}{\textwidth}{X r}
      \textbf{\href{#5}{#1}} & \textit{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabularx}{\textwidth}{X r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabularx}{\textwidth}{X r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabularx}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabularx}{\textwidth}{X r}
      \small\href{#2}{\textbf{#1}} & {} \\
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{\textwidth}{X r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% New command to add projects under Experience
\newcommand{\resumeProject}[3]{
    \item[$\bullet$] \textbf{\href{#2}{#1}}: \small #3 \par
}

% Resume starts here
\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Abdel-Rhman Khamis} \\ \vspace{.5pt}
    \small
    \faPhone \hspace{.5pt} \faWhatsapp \hspace{.5pt} \href{https://wa.me/+201153015763}{\textcolor{NavyBlue}{+201153015763}}
    $|$
    \faCertificate \hspace{.5pt} \href{https://www.credly.com/users/abdelrhman-khamis}{\textcolor{NavyBlue}{Certifications}}
    $|$
    \Email \hspace{.5pt} \href{mailto:Abdelrhman.khamis.alex@gmail.com}{\textcolor{NavyBlue}{Abdelrhman.khamis.alex@gmail.com}}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://linkedin.com/in/abdelrhman-khamis}{\textcolor{NavyBlue}{LinkedIn}}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/abdelrhman-kh}{\textcolor{NavyBlue}{GitHub}}
    $|$
    \Mundus \hspace{.5pt} \href{https://abdelrhman.khamis.work}{\textcolor{NavyBlue}{Portfolio}}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Alexandria,+Egypt}{\textcolor{NavyBlue}{Egypt}}
\end{center}
\vspace{-20pt}
%----------- SUMMARY -----------
\section*{\textbf{Summary}}
\resumeSubHeadingListStart
\item {
  DevOps engineer with over 3 years of experience in development and operations, and 2.5 years as a System Administrator. Good with Git, Docker, Kubernetes, and cloud platforms like AWS, Azure, and Oracle Cloud. Skilled in CI/CD and Linux security. Enjoys solving problems and working with others.
}
\resumeSubHeadingListEnd

\vspace{-20pt}
%----------- EXPERIENCE -----------
\section*{\textbf{Experience}}
\resumeSubHeadingListStart

\vspace{-5pt}

\resumeSubheading
{\textcolor{NavyBlue}{BlackStone eIT}}{Abu Dhabi, UAE}
{\textbf{Senior DevOps Engineer}}{Feb 2025 - Present}
{https://www.blackstoneeit.com}
\resumeItemListStart
\resumeItem{Collaborated with high-profile clients, including the United Arab Emirates Government, resulting in a 25\% increase in system efficiency.}
\resumeItemListEnd

\vspace{-3pt}
\hspace{10pt}
\vspace{2pt}
\textbf{Projects:}
\resumeItemListStart
\vspace{-10pt}
\resumeProject {\textcolor{NavyBlue}{Abu Dhabi Housing Authority}}{https://dub.ai/en/omp/}{Used DevSecOps with Kubernetes for secure and automated deployments.}
\vspace{0pt}
\resumeItemListEnd

\vspace{-15pt}

\resumeSubheading
{\textcolor{NavyBlue}{Meem Development}}{Alexandria, Egypt}
{\textbf{DevOps Engineer}}{Nov 2023 - March 2025}
{https://www.meemdev.com}
\resumeItemListStart
\resumeItem{Implemented CI/CD pipelines using GitHub, Jenkins, and Azure DevOps.}
\resumeItem{Engineered scalable ERP systems on AWS and Oracle Cloud, integrating DevSecOps and GitOps.}
\resumeItem{Collaborated with high-profile clients, including the Saudi Government, resulting in a 30\% increase in system efficiency.}
\resumeItemListEnd

\vspace{-3pt}
\hspace{10pt}
\vspace{2pt}
\textbf{Projects:}
\resumeItemListStart
\vspace{-10pt}
\resumeProject {\textcolor{NavyBlue}{Dubai Future Foundation - One Million Prompts}}{https://dub.ai/en/omp/}{Used DevSecOps and GitOps with Kubernetes for secure and automated deployments. Applied blue-green deployment for smooth updates and auto-scaling for better performance. Managed infrastructure with Terraform to speed up disaster recovery (DR) and improve security, monitoring, and reliability.}
\vspace{-2pt}
\resumeProject {\textcolor{NavyBlue}{Mshfa - SaaS Healthcare Platform}}{https://mshfakwt.com/}{Integrated DevSecOps and GitOps with Kubernetes to automate and secure deployments. Improved system reliability, security, and monitoring, ensuring a stable and efficient healthcare platform.}
\vspace{-2pt}
\resumeProject {\textcolor{NavyBlue}{General Entertainment Authority - Saudi Esports Federation
 Academy}}{https://sea.sa/}{Implemented DevSecOps and GitOps with Kubernetes for secure and automated deployments. Used blue-green deployment for zero-downtime releases and auto-scaling to handle traffic changes. Improved security, monitoring, and system reliability for esports operations.}
\vspace{-2pt}
\resumeProject {\textcolor{NavyBlue}{Terraform-Azure-PrivateInfra}}{https://github.com/abdelrhman-kh/Terraform-Azure-PrivateInfra}{Provisioned a production-ready Azure infrastructure with Terraform and private networking.}
\resumeItemListEnd

\vspace{-15pt}
\resumeSubheading
{\textcolor{NavyBlue}{Andalusia Healthcare Business Solutions}}{Alexandria, Egypt}
{\textbf{DevOps Engineer}}{Oct 2022 - Nov 2023}
{https://www.ahbs.tech}
\resumeItemListStart
\resumeItem{Managed TFS Server for CI/CD, including blue-green and canary deployments.}
\resumeItem{Developed a horizontally scalable ERP system on AWS for a monolithic architecture, reducing deployment time by 25\%.}
\resumeItem{Supported multiple Scrum teams and Agile processes across various products, improving team productivity by 20\%.}
\resumeItemListEnd

\vspace{-3pt}
\hspace{10pt}
\vspace{2pt}
\textbf{Projects:}
\resumeItemListStart
\vspace{-10pt}
\resumeProject {\textcolor{NavyBlue}{KubernetesOnPremise}}{https://github.com/abdelrhman-kh/KubernetesOnPremise}{Automated Kubernetes cluster setup with Flannel, Dashboard, MetalLB, and Metrics Server.}
\vspace{-2pt}
\resumeProject {\textcolor{NavyBlue}{RunSqlScriptProgram}}{https://github.com/abdelrhman-kh/RunSqlScriptProgram}{Developed a .NET MVC 6.0 app for managing MSSQL connection strings and executing MSSQL scripts on selected database instances, enhancing database management efficiency.}
\resumeItemListEnd

\vspace{-15pt}
\resumeSubheading
{\textcolor{NavyBlue}{Code Zone}}{Alexandria, Egypt}
{}{}
{https://www.codezone-eg.com}
\vspace{-33pt}
\resumeSubSubheading{\textbf{DevOps Engineer}}{Sep 2021 - Sep 2022}
\resumeItemListStart
\resumeItem{Managed Azure DevOps for CI/CD with safe deployment methods.
Used Docker and Kubernetes on DigitalOcean; automated tasks with scripts to cut down mistakes.
Worked on AWS Lambda, SQL, and Windows services using .NET Core 6.0 to make the system faster.}
\resumeItemListEnd

\vspace{-3pt}
\hspace{10pt}
\vspace{2pt}
\textbf{Projects:}
\resumeItemListStart
\vspace{-10pt}
\resumeProject {\textcolor{NavyBlue}{TerraformCreateEC2Instance}}{https://github.com/abdelrhman-kh/terraform-create-ec2-instance}{Created a Terraform project to automate EC2 instance creation and configuration, streamlining AWS infrastructure deployment and reducing setup time by 50\%.}
\vspace{-2pt}
\resumeProject {\textcolor{NavyBlue}{LambdaFunctionNotifiedSNSSubscription}}{https://github.com/abdelrhman-kh/lambda-function-notified-sns-subscription}{Developed an AWS Lambda function to monitor CloudWatch logs of another Lambda function and trigger SNS notifications upon activity, enhancing monitoring and alerting capabilities.}
\resumeItemListEnd

\vspace{-20pt}
\resumeSubSubheading{\textbf{System Administrator}}{Jul 2019 - Sep 2021}
\resumeItemListStart
\resumeItem{Improved network, VoIP, and email servers to work better.
Set up and managed ERP, systems, and security.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-15pt}
%----------- SKILLS -----------
\section*{\textbf{Skills}}
\resumeSubHeadingListStart
\item{
\textbf{DevOps Stack:} Git, Jenkins, Azure DevOps, GitHub, Octopus Deploy, Helm, ArgoCD, RabbitMQ, PowerShell, Bash, Docker (Compose, Swarm), Kubernetes.
}
\vspace{-5pt}
\item{
\textbf{Monitoring and Logging:} ELK Stack, Zabbix, Prometheus, Loki, Grafana, DataDog.
}
\vspace{-5pt}
\item{
\textbf{Database Administration:} MSSQL, PostgreSQL, MySQL, MariaDB, MongoDB.
} 
\vspace{-5pt}
\item{
\textbf{Cloud Providers:} AWS, Azure, GCP, DigitalOcean, Oracle Cloud, Zain Cloud.
}
\resumeSubHeadingListEnd

\vspace{-20pt}
%----------- PROJECTS -----------
% \section*{\textbf{Projects}}

% \vspace{-7pt}
% \resumeSubHeadingListStart
% \resumeProjectHeading
%     {\textbf{KubernetesOnPremise}}
%     {https://github.com/abdelrhman-kh/KubernetesOnPremise}
% \resumeItemListStart
% \resumeItem{Automated on-premises Kubernetes cluster installation, supporting various versions and essential assets like Flannel, Dashboard, MetalLB, and Metrics Server.}
% \resumeItemListEnd
% \resumeSubHeadingListEnd

% \vspace{-27pt}

% \resumeSubHeadingListStart
% \resumeProjectHeading
%     {\textbf{RunSqlScriptProgram}}
%     {https://github.com/abdelrhman-kh/RunSqlScriptProgram}
% \resumeItemListStart
% \resumeItem{Developed a .NET MVC 6.0 app for managing MSSQL connection strings and executing MSSQL scripts on selected database instances, enhancing database management efficiency.}
% \resumeItemListEnd
% \resumeSubHeadingListEnd

% \vspace{-27pt}

% \resumeSubHeadingListStart
% \resumeProjectHeading
%     {\textbf{TerraformCreateEC2Instance}}
%     {https://github.com/abdelrhman-kh/terraform-create-ec2-instance}
% \resumeItemListStart
% \resumeItem{Created a Terraform project to automate EC2 instance creation and configuration, streamlining AWS infrastructure deployment and reducing setup time by 50\%.}
% \resumeItemListEnd
% \resumeSubHeadingListEnd

% \vspace{-27pt}

% \resumeSubHeadingListStart
% \resumeProjectHeading
%     {\textbf{LambdaFunctionNotifiedSNSSubscription}}
%     {https://github.com/abdelrhman-kh/lambda-function-notified-sns-subscription}
% \resumeItemListStart
% \resumeItem{Developed an AWS Lambda function to monitor CloudWatch logs of another Lambda function and trigger SNS notifications upon activity, enhancing monitoring and alerting capabilities.}
% \resumeItemListEnd
% \resumeSubHeadingListEnd

% \vspace{-27pt}

% \resumeSubHeadingListStart
% \resumeProjectHeading
%     {\textbf{Terraform-Azure-PrivateInfra}}
%     {https://github.com/abdelrhman-kh/Terraform-Azure-PrivateInfra}
% \resumeItemListStart
% \resumeItem{This repository contains a Terraform project for provisioning a production-ready Azure infrastructure with App Services, MySQL, Redis, Blob Storage, and an Application Gateway, emphasizing security and scalability through private networking.}
% \resumeItemListEnd
% \resumeSubHeadingListEnd

\end{document}

% \vspace{-5pt}

% % ----------- EDUCATION -----------
% \section*{\textbf{Education}}

% \resumeSubHeadingListStart
% \resumeEducationHeading
% {Bachelor of Business/Commerce, General}{Nov 2023 - 2027}
% {Damanhour University}{Damanhour, Egypt}{}{}
% \resumeSubHeadingListEnd


