\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

% Uncomment the desired font
\usepackage[sfdefault]{FiraSans}
\usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}
\usepackage{CormorantGaramond}
\usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% Modified to include URL for company name
\newcommand{\resumeSubheading}[5]{
  \vspace{-2pt}\item
    \begin{tabularx}{\textwidth}{X r}
      \textbf{\href{#5}{#1}} & \textit{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabularx}{\textwidth}{X r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabularx}{\textwidth}{X r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabularx}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabularx}{\textwidth}{X r}
      \small\href{#2}{\textbf{#1}} & {} \\
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{\textwidth}{X r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabularx}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Resume starts here
\begin{document}

%---------- HEADING ----------
\begin{center}
    \textbf{\Huge \scshape Abdel-Rhman Khamis} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:+201153015763}{+201153015763}
    $|$
    \faCalendar \hspace{.5pt} \href{https://howlongagogo.com/date/1998/november/21}{21-November-1998}
    $|$
    \Email \hspace{.5pt} \href{mailto:Abdelrhman.khamis.alex@gmail.com}{Abdelrhman.khamis.alex@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://linkedin.com/in/abdelrhman-khamis}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/abdelrhman-kh}{GitHub}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/Alexandria,+Egypt}{Alexandria, Egypt}
\end{center}

%----------- SUMMARY -----------
\section*{\textbf{Summary}}
\resumeSubHeadingListStart
\item {
DevOps Engineer with 3 years of experience in software development and system operations. Previously a System Administrator for 2.5 years. Skilled with Git, Docker, Kubernetes, and cloud services like AWS, Azure, and Oracle Cloud. Good at setting up CI/CD pipelines and securing Linux systems. Enjoys problem-solving and working with teams to create excellent software.
}
\resumeSubHeadingListEnd

\vspace{-15pt}
%----------- EXPERIENCE -----------
\section*{\textbf{Experience}}
\resumeSubHeadingListStart

\resumeSubheading
{Meem Development}{Alexandria, Egypt}
{\textbf{DevOps Engineer}}{Nov 2023 - Present}
{https://www.meemdev.com}  % URL for Meem Company
\resumeItemListStart
\resumeItem{Orchestrated CI/CD pipelines using GitHub, Jenkins, and Azure DevOps, mastering blue-green and canary deployments. Engineered scalable ERP systems on AWS and Oracle Cloud, seamlessly integrating DevSecOps and GitOps for both monolithic and microservices architectures. Collaborated with high-profile clients, including the Saudi Government, and contributed to diverse projects across multiple levels.}
% \resumeItem{Automated infrastructure deployment, cutting manual errors by 50\%.}
% \resumeItem{Secured Linux systems, ensuring high availability and reliability.}
\resumeItemListEnd

\resumeSubheading
{Andalusia Healthcare Business Solutions}{Alexandria, Egypt}
{\textbf{DevOps Engineer}}{Oct 2022 - Nov 2023}
{https://www.ahbs.tech}  % URL for AHBS Company
\resumeItemListStart
\resumeItem{Set up and managed TFS Server for CI/CD, including blue-green and canary deployments. Implemented a horizontally scalable ERP system on AWS for a monolithic architecture, supporting multiple Scrum teams and Agile processes across various products.}
\resumeItemListEnd

% Main heading for the company with multiple roles
\resumeSubheading
{Code Zone}{Alexandria, Egypt}
{}{}
{https://www.codezone-eg.com}  % URL for Code Zone Company
\vspace{-33pt} % Remove extra space
% First job role
\resumeSubSubheading{\textbf{DevOps Engineer}}{Sep 2021 - Sep 2022}
\resumeItemListStart
\resumeItem{Set up and managed Azure DevOps Server for CI/CD, blue-green, and canary deployments. Implemented Docker and Kubernetes on DigitalOcean and automated infrastructure with Bash and PowerShell scripts.}
\resumeItem{Administered AWS Lambda functions in Python, SQL databases, and Windows services for the Egyptian Invoice project using .NET Core 6.0. Managed ERP systems on-premises and in the cloud using Agile and Kanban.}
% \resumeItem{Developed infrastructure and monitoring tools, enhancing system stability.}
\resumeItemListEnd
\vspace{-15pt} % Remove extra space
% Second job role
\resumeSubSubheading{\textbf{System Administrator}}{Jul 2019 - Sep 2021}
\resumeItemListStart
\resumeItem{Provided comprehensive technical support, optimized workstation and LAN performance, and administered VoIP systems and Exchange mail servers.}
\resumeItem{Deployed and maintained ERP systems, network infrastructure, and camera systems, while training users on system functionalities.}
% \resumeItem{Participated in containerization efforts using Docker and Kubernetes.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-15pt}
%----------- SKILLS -----------
\section*{\textbf{Skills}}
\resumeSubHeadingListStart
\item{
\textbf{Technical Proficiency:} vSphere, ELK Stack, Zabbix, Prometheus, Loki, Grafana, Kubernetes, Docker (Docker-Compose, Docker-Swarm), PowerShell, Bash, TFS, Azure DevOps, Jenkins, GitHub, Octopus Deploy, Git, Helm, ArgoCD, RabbitMQ, MSSQL, PostgreSQL, MySQL, MariaDB, MongoDB (Database Administration).
}
\item{
\textbf{Cloud Providers:} AWS, Azure, DigitalOcean, Oracle Cloud, Zain Cloud
}
\resumeSubHeadingListEnd

\vspace{-10pt}
%----------- PROJECT -----------
\section*{\textbf{Project}}

\vspace{-5pt}
\resumeSubHeadingListStart
\resumeProjectHeading
    {\textbf{KubernetesOnPremise}}
    {https://github.com/abdelrhman-kh/KubernetesOnPremise}
\resumeItemListStart
\resumeItem{Automates on-premises Kubernetes cluster installation and setup, supporting various versions and essential assets like Flannel, Dashboard, MetalLB, and Metrics Server.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-25pt}

\resumeSubHeadingListStart
\resumeProjectHeading
    {\textbf{RunSqlScriptProgram}}
    {https://github.com/abdelrhman-kh/RunSqlScriptProgram}
\resumeItemListStart
\resumeItem{Developed a .NET MVC 6.0 app using a code-first approach, designed to aid DevOps teams in managing MSSQL connection strings with CRUD operations and executing MSSQL scripts on chosen database instances.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\vspace{-25pt}

\resumeSubHeadingListStart
\resumeProjectHeading
    {\textbf{TerraformCreateEC2Instance}}
    {https://github.com/abdelrhman-kh/terraform-create-ec2-instance}
\resumeItemListStart
\resumeItem{Developed a project using Terraform to automate the creation and configuration of EC2 instances, streamlining infrastructure deployment on AWS.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%----------- EDUCATION -----------
\section*{\textbf{Education}}

\resumeSubHeadingListStart
\resumeEducationHeading
{Bachelor of Business/Commerce, General}{Nov 2023 - 2027}
{Damanhour University}{Damanhour, Egypt}{}{}
\resumeSubHeadingListEnd

\end{document}
